Predicting computational reproducibility of data analysis pipelines \\in large population studies using collaborative filtering

### 2018-07-26 paper.tex
Added a figure generation script, updated README, now generate all figures in pdf directly, fixed typos

\begin{figure}[h!]
        \centering
        \begin{subfigure}[b]{0.4\linewidth}
                  \includegraphics[width=\columnwidth]{figures/5vs7_columns_04_training}
                  \caption{Complete Columns}
                  \label{fig:Columns-Sample-Training-set}
        \end{subfigure}
        \begin{subfigure}[b]{0.4\linewidth}
                  \includegraphics[width=\columnwidth]{figures/5vs7_rows_04_training}
                  \caption{Complete Rows}
                  \label{fig:Rows-Sample-Training-set}
        \end{subfigure}
        \begin{subfigure}[b]{0.4\linewidth}
                 \includegraphics[width=\columnwidth]{figures/5vs7_random-real_04_training}
                \caption{Random Subjects (RS)}
                  \label{fig:Uniform-S-Sample-Training-set}
        \end{subfigure}
        \begin{subfigure}[b]{0.4\linewidth}
                  \includegraphics[width=\columnwidth]{figures/5vs7_diagonal_04_training}
                  \caption{RFNU}
                  \label{fig:Diagonal-Sample-Training-set}
        \end{subfigure}
        \begin{subfigure}[b]{0.4\linewidth}
                  \includegraphics[width=\columnwidth]{figures/5vs7_random-triangular-largest_04_training}
                  \caption{RFNTL}
                  \label{fig:triangular-L-Sample-Training-set}
        \end{subfigure}
        \begin{subfigure}[b]{0.4\linewidth}
                  \includegraphics[width=\columnwidth]{figures/5vs7_random-triangular-smallest_04_training}
                  \caption{RFNTS}
                  \label{fig:triangular-S-Sample-Training-set}
        \end{subfigure}
        \begin{subfigure}[b]{0.4\linewidth}
        \includegraphics[width=\columnwidth]{figures/5vs7_random-unreal_04_training}
                  \caption{Random Unreal}
                  \label{fig:Random-Unreal-Sample-Training-set}
        \end{subfigure}
        \caption{Sample training set for different methods with a training ratio of 0.4.}
        \label{fig:sampling}
\end{figure}

@@

\begin{figure}
\centering
        %\begin{subfigure}[b]{0.4\linewidth}
                  %\includegraphics[width=\columnwidth]{data/Utility_Matrix/Synthetic/synthetic_subject_types/1_SubjectType_utility_matrix.png}
                  %\caption{1 type}
        %\end{subfigure}
        \begin{subfigure}[b]{0.4\linewidth}
                  \includegraphics[width=\columnwidth]{data/Utility_Matrix/Synthetic/synthetic_subject_types/2_SubjectType_utility_matrix.png}
                  \caption{2 types}
        \end{subfigure}
        \begin{subfigure}[b]{0.4\linewidth}
                  \includegraphics[width=\columnwidth]{data/Utility_Matrix/Synthetic/synthetic_subject_types/4_SubjectType_utility_matrix.png}
                  \caption{4 types}
        \end{subfigure}
                \begin{subfigure}[b]{0.4\linewidth}
                  \includegraphics[width=\columnwidth]{data/Utility_Matrix/Synthetic/synthetic_subject_types/8_SubjectType_utility_matrix.png}
                  \caption{8 types}
        \end{subfigure}
                \begin{subfigure}[b]{0.4\linewidth}
                  \includegraphics[width=\columnwidth]{data/Utility_Matrix/Synthetic/synthetic_subject_types/16_SubjectType_utility_matrix.png}
                  \caption{16 types}
        \end{subfigure}
                \begin{subfigure}[b]{0.4\linewidth}
                  \includegraphics[width=\columnwidth]{data/Utility_Matrix/Synthetic/synthetic_subject_types/32_SubjectType_utility_matrix.png}
                  \caption{32 types}
        \end{subfigure}
                \begin{subfigure}[b]{0.4\linewidth}
                  \includegraphics[width=\columnwidth]{data/Utility_Matrix/Synthetic/synthetic_subject_types/64_SubjectType_utility_matrix.png}
                  \caption{64 types}
        \end{subfigure}
\caption{Synthetic reproducibility matrices. White cells denote reproducibility errors.}
\label{fig:synthetic-data}
\end{figure}

@@

We collected data to evaluate the computational reproducibility of analysis
pipelines of the Human Connectome Project~\cite{glasser2013minimal}. We
processed a set S of 94 subjects randomly selected in the S500 HCP
release\footnote{\url{https://db.humanconnectome.org}} in three execution conditions with different
versions of the CentOS operating system (5.\todo{?}, 6.8 and 7.2), using the
PreFreesurfer and Freesurfer pipelines described 
in~\cite{glasser2013minimal} and available on 
GitHub\footnote{\url{https://github.com/Washington-University/Pipelines/releases/tag/v3.19.0}}. 
For each pipeline, we identified the set F of files produced for all
subjects in all conditions. For each condition pair and each pipeline, 
we computed a binary reproducibility matrix U of size $|F|\times|S|$, 
where $U_{i,j}$ is true iif file $i$ of subject $j$ was different in 
each condition. Rows of $U$ were ordered by ascending file modification 
time in a random subject in S.

@@

\begin{figure}[h!]
  \centering
  \begin{subfigure}[b]{0.45\linewidth}
        \includegraphics[width=\columnwidth]{data/Utility_Matrix/PreFreeSurfer/PFS_5v6_utility_matrix.png}
  \caption{PFS, C5 vs C6}
  \end{subfigure}
  \begin{subfigure}[b]{0.45\linewidth}
         \includegraphics[width=\columnwidth]{data/Utility_Matrix/PreFreeSurfer/PFS_5v7_utility_matrix.png}
  \caption{PFS, C5 vs C7}
  \end{subfigure}
  \begin{subfigure}[b]{0.45\linewidth}
        \includegraphics[width=\columnwidth]{data/Utility_Matrix/PreFreeSurfer/PFS_6v7_utility_matrix.png}
  \caption{PFS, C6 vs C7}
  \end{subfigure}
  \begin{subfigure}[b]{0.45\linewidth}
        \includegraphics[width=\columnwidth]{data/Utility_Matrix/FS-100files/FS-First-bound-100files.png}
  \caption{FS (first 100 files), C6 vs C7}
  \end{subfigure}
  \caption{Utility matrices, PreFreesurfer (PFS) and Freesurfer (FS) pipelines}
    \label{fig:utility-matrices}
\end{figure}

@@

Accuracy results for the different numbers of subject types are 
reported in Figure~\ref{fig:results-synthetic}. By construction, the 
accuracy of the dummy classifier is close to 0.5 for all subject types. Random 
Unreal performs very well for all subject types, which confirms that 
ALS is working correctly. Unsurprisingly, all the other methods perform 
better than the dummy classifier, and their accuracy decreases as the 
number of subject types increases.

However, only 3 methods are able to provide accuracy values above 0.85 
for all subject types: Random Subjects (RS), RFNU and RFNTL. This is 
due to the fact that these methods are the only ones that can sample 
files produced toward the end of the execution while maintaining a 
reduced number of empty columns. Surprisingly, RFNTS does not perform 
well for more than 2 subject types \todo{Check that.}.

@@

\begin{figure*}
\begin{subfigure}[b]{0.4\linewidth}
        \includegraphics[width=0.8\columnwidth, angle=-90]{data/results/means_of_results/ALS/Synthetic/synthetic_subject_types/ALS-2-types.pdf}
        \caption{2 subject types}
\end{subfigure}
\begin{subfigure}[b]{0.4\linewidth}
        \includegraphics[width=0.8\columnwidth, angle=-90]{data/results/means_of_results/ALS/Synthetic/synthetic_subject_types/ALS-4-types.pdf}
        \caption{4 subject types}
\end{subfigure}
\begin{subfigure}[b]{0.4\linewidth}
        \includegraphics[width=0.8\columnwidth, angle=-90]{data/results/means_of_results/ALS/Synthetic/synthetic_subject_types/ALS-8-types.pdf}
        \caption{8 subject types}
\end{subfigure}
\begin{subfigure}[b]{0.4\linewidth}
        \includegraphics[width=0.8\columnwidth, angle=-90]{data/results/means_of_results/ALS/Synthetic/synthetic_subject_types/ALS-16-types.pdf}
        \caption{16 subject types}
\end{subfigure}
\begin{subfigure}[b]{0.4\linewidth}
        \includegraphics[width=0.8\columnwidth, angle=-90]{data/results/means_of_results/ALS/Synthetic/synthetic_subject_types/ALS-32-types.pdf}
        \caption{32 subject types}
\end{subfigure}
\hfill
\begin{subfigure}[b]{0.4\linewidth}
        \includegraphics[width=0.8\columnwidth, angle=-90]{data/results/means_of_results/ALS/Synthetic/synthetic_subject_types/ALS-64-types.pdf}
        \caption{64 subject types}
\end{subfigure}
\caption{Accuracy results on synthetic data, ALS \emph{without} bias.}
\label{fig:results-synthetic}
\end{figure*}

@@

\begin{figure*}
\begin{subfigure}[b]{0.4\linewidth}
        \includegraphics[width=0.8\columnwidth, angle=-90]{data/results/means_of_results/ALS-Bias/Synthetic/synthetic_subject_types/ALS-Bias-2-types.pdf}
        \caption{2 subject types}
\end{subfigure}
\begin{subfigure}[b]{0.4\linewidth}
        \includegraphics[width=0.8\columnwidth, angle=-90]{data/results/means_of_results/ALS-Bias/Synthetic/synthetic_subject_types/ALS-Bias-4-types.pdf}
        \caption{4 subject types}
\end{subfigure}
\begin{subfigure}[b]{0.4\linewidth}
        \includegraphics[width=0.8\columnwidth, angle=-90]{data/results/means_of_results/ALS-Bias/Synthetic/synthetic_subject_types/ALS-Bias-8-types.pdf}
        \caption{8 subject types}
\end{subfigure}
\begin{subfigure}[b]{0.4\linewidth}
        \includegraphics[width=0.8\columnwidth, angle=-90]{data/results/means_of_results/ALS-Bias/Synthetic/synthetic_subject_types/ALS-Bias-16-types.pdf}
        \caption{16 subject types}
\end{subfigure}
\begin{subfigure}[b]{0.4\linewidth}
        \includegraphics[width=0.8\columnwidth, angle=-90]{data/results/means_of_results/ALS-Bias/Synthetic/synthetic_subject_types/ALS-Bias-32-types.pdf}
        \caption{32 subject types}
\end{subfigure}
\hfill
\begin{subfigure}[b]{0.4\linewidth}
        \includegraphics[width=0.8\columnwidth, angle=-90]{data/results/means_of_results/ALS-Bias/Synthetic/synthetic_subject_types/ALS-Bias-64-types.pdf}
        \caption{64 subject types}
\end{subfigure}
\caption{Accuracy results on synthetic data, ALS \emph{with} bias.}
\label{fig:results-synthetic-als-bias}
\end{figure*}

@@

Results for ALS without bias are reported in 
Figure~\ref{fig:results-real-als}. Among the methods that performed 
well in the synthetic dataset, RFNU performs the best, with an accuracy
higher than 0.95 \todo{check value} for all datasets, when the training ratio is larger than 0.5. RS and RFNTL
are slightly underperforming compared to RFNU.
Complete rows and complete columns do not even reach the accuracy of the 
dummy classifier. The reference method, Random Unreal, has an accuracy close
to 1, which shows that collaborative filtering works well on this dataset too.

\begin{figure*}
\begin{subfigure}[b]{0.4\linewidth}
        \includegraphics[width=0.8\columnwidth, angle=-90]{data/results/means_of_results/ALS/PreFreeSurfer/ALS-PFS-5v6.pdf}
        \caption{PFS, CentOS5 vs CentOS6}
\end{subfigure}
\begin{subfigure}[b]{0.4\linewidth}
        \includegraphics[width=0.8\columnwidth, angle=-90]{data/results/means_of_results/ALS/PreFreeSurfer/ALS-PFS-5v7.pdf}
        \caption{PFS, CentOS5 vs CentOS7}
\end{subfigure}
\begin{subfigure}[b]{0.4\linewidth}
        \includegraphics[width=0.8\columnwidth, angle=-90]{data/results/means_of_results/ALS/PreFreeSurfer/ALS-PFS-6v7.pdf}
        \caption{PFS, CentOS6 vs CentOS7}
\end{subfigure}\hfill
\begin{subfigure}[b]{0.4\linewidth}
        \includegraphics[width=0.8\columnwidth, angle=-90]{data/results/means_of_results/ALS/FS-100files/ALS-FS100files.pdf}
        \caption{FS, CentOS6 vs CentOS7}
\end{subfigure}
\caption{Accuracy results on PreFresurfer (PFS) and Freesurfer (FS) data, ALS \emph{without} bias.}
\label{fig:results-real-als}
\end{figure*}

@@

\begin{figure*}
\begin{subfigure}[b]{0.4\linewidth}
        \includegraphics[width=0.8\columnwidth, angle=-90]{data/results/means_of_results/ALS-Bias/PreFreeSurfer/ALS-Bias-PFS-5v6.pdf}
        \caption{PFS, CentOS5 vs CentOS6}
\end{subfigure}
\begin{subfigure}[b]{0.4\linewidth}
        \includegraphics[width=0.8\columnwidth, angle=-90]{data/results/means_of_results/ALS-Bias/PreFreeSurfer/ALS-Bias-PFS-5v7.pdf}
        \caption{PFS, CentOS5 vs CentOS7}
        \label{fig:pfs-c5vsc7-bias}
\end{subfigure}
\begin{subfigure}[b]{0.4\linewidth}
        \includegraphics[width=0.8\columnwidth, angle=-90]{data/results/means_of_results/ALS-Bias/PreFreeSurfer/ALS-Bias-PFS-6v7.pdf}
        \caption{PFS, CentOS6 vs CentOS7}
\end{subfigure}\hfill
\begin{subfigure}[b]{0.4\linewidth}
        \includegraphics[width=0.8\columnwidth, angle=-90]{data/results/means_of_results/ALS-Bias/FS-100files/ALS-Bias-FS100files.pdf}
        \caption{FS, CentOS6 vs CentOS7}
\end{subfigure}
\caption{Accuracy results on PreFresurfer (PFS) and Freesurfer (FS) data, ALS \emph{with} bias.}
\label{fig:results-real-als-bias}
\end{figure*}

>>>>

\begin{figure}[h!]
        \centering
        \begin{subfigure}[b]{0.45\columnwidth}
                  \includegraphics[width=\columnwidth]{figures/5vs7_columns_04_training}
                  \caption{Complete Columns}
                  \label{fig:Columns-Sample-Training-set}
        \end{subfigure}
        \begin{subfigure}[b]{0.45\columnwidth}
                  \includegraphics[width=\columnwidth]{figures/5vs7_rows_04_training}
                  \caption{Complete Rows}
                  \label{fig:Rows-Sample-Training-set}
        \end{subfigure}
        \begin{subfigure}[b]{0.45\columnwidth}
                 \includegraphics[width=\columnwidth]{figures/5vs7_random-real_04_training}
                \caption{Random Subjects (RS)}
                  \label{fig:Uniform-S-Sample-Training-set}
        \end{subfigure}
        \begin{subfigure}[b]{0.45\columnwidth}
                  \includegraphics[width=\columnwidth]{figures/5vs7_diagonal_04_training}
                  \caption{RFNU}
                  \label{fig:Diagonal-Sample-Training-set}
        \end{subfigure}
        \begin{subfigure}[b]{0.45\columnwidth}
                  \includegraphics[width=\columnwidth]{figures/5vs7_random-triangular-largest_04_training}
                  \caption{RFNTL}
                  \label{fig:triangular-L-Sample-Training-set}
        \end{subfigure}
        \begin{subfigure}[b]{0.45\columnwidth}
                  \includegraphics[width=\columnwidth]{figures/5vs7_random-triangular-smallest_04_training}
                  \caption{RFNTS}
                  \label{fig:triangular-S-Sample-Training-set}
        \end{subfigure}
        \begin{subfigure}[b]{\columnwidth}
        \centering
        \includegraphics[width=0.45\columnwidth]{figures/5vs7_random-unreal_04_training}
                  \caption{Random Unreal}
                  \label{fig:Random-Unreal-Sample-Training-set}
        \end{subfigure}
        \caption{Sample training set for different methods with a training ratio of 0.4.}
        \label{fig:sampling}
\end{figure}

@@

\begin{figure}
\centering
        %\begin{subfigure}[b]{\columnwidth}
                  %\includegraphics[width=\columnwidth]{data/Utility_Matrix/Synthetic/synthetic_subject_types/1_SubjectType_utility_matrix.png}
                  %\caption{1 type}
        %\end{subfigure}
        \begin{subfigure}[b]{0.45\columnwidth}
                  \includegraphics[width=\columnwidth]{data/Utility_Matrix/Synthetic/synthetic_subject_types/2_SubjectType_utility_matrix.png}
                  \caption{2 types}
        \end{subfigure}
        \begin{subfigure}[b]{0.45\columnwidth}
                  \includegraphics[width=\columnwidth]{data/Utility_Matrix/Synthetic/synthetic_subject_types/4_SubjectType_utility_matrix.png}
                  \caption{4 types}
        \end{subfigure}
                \begin{subfigure}[b]{0.45\columnwidth}
                  \includegraphics[width=\columnwidth]{data/Utility_Matrix/Synthetic/synthetic_subject_types/8_SubjectType_utility_matrix.png}
                  \caption{8 types}
        \end{subfigure}
                \begin{subfigure}[b]{0.45\columnwidth}
                  \includegraphics[width=\columnwidth]{data/Utility_Matrix/Synthetic/synthetic_subject_types/16_SubjectType_utility_matrix.png}
                  \caption{16 types}
        \end{subfigure}
                \begin{subfigure}[b]{0.45\columnwidth}
                  \includegraphics[width=\columnwidth]{data/Utility_Matrix/Synthetic/synthetic_subject_types/32_SubjectType_utility_matrix.png}
                  \caption{32 types}
        \end{subfigure}
                \begin{subfigure}[b]{0.45\columnwidth}
                  \includegraphics[width=\columnwidth]{data/Utility_Matrix/Synthetic/synthetic_subject_types/64_SubjectType_utility_matrix.png}
                  \caption{64 types}
        \end{subfigure}
\caption{Synthetic reproducibility matrices. White cells denote reproducibility errors.}
\label{fig:synthetic-data}
\end{figure}

@@

We collected data to evaluate the computational reproducibility of analysis
pipelines of the Human Connectome Project~\cite{glasser2013minimal}. We
processed a set S of 94 subjects randomly selected in the S500 HCP
release\footnote{\url{https://db.humanconnectome.org}} in three execution conditions with different
versions of the CentOS operating system (5.11, 6.8 and 7.2), using the
PreFreesurfer and Freesurfer pipelines described 
in~\cite{glasser2013minimal} and available on 
GitHub\footnote{\url{https://github.com/Washington-University/Pipelines/releases/tag/v3.19.0}}. 
For each pipeline, we identified the set F of files produced for all
subjects in all conditions. For each condition pair and each pipeline, 
we computed a binary reproducibility matrix U of size $|F|\times|S|$, 
where $U_{i,j}$ is true iif file $i$ of subject $j$ was different in 
each condition. Rows of $U$ were ordered by ascending file modification 
time in a random subject in S.

@@

\begin{figure}[h!]
  \centering
  \begin{subfigure}[b]{0.45\columnwidth}
        \includegraphics[width=\columnwidth]{data/Utility_Matrix/PreFreeSurfer/PFS_5v6_utility_matrix.png}
  \caption{PFS, C5 vs C6}
  \end{subfigure}
  \begin{subfigure}[b]{0.45\columnwidth}
         \includegraphics[width=\columnwidth]{data/Utility_Matrix/PreFreeSurfer/PFS_5v7_utility_matrix.png}
  \caption{PFS, C5 vs C7}
  \end{subfigure}
  \begin{subfigure}[b]{0.45\columnwidth}
        \includegraphics[width=\columnwidth]{data/Utility_Matrix/PreFreeSurfer/PFS_6v7_utility_matrix.png}
  \caption{PFS, C6 vs C7}
  \end{subfigure}
  \begin{subfigure}[b]{0.45\columnwidth}
        \includegraphics[width=\columnwidth]{data/Utility_Matrix/FS-100files/FS-First-bound-100files.png}
  \caption{FS (100 files), C6 vs C7}
  \end{subfigure}
  \caption{Utility matrices, PreFreesurfer (PFS) and Freesurfer (FS) pipelines}
    \label{fig:utility-matrices}
\end{figure}

@@

Accuracy results for the different numbers of subject types are 
reported in Figure~\ref{fig:results-synthetic}. By construction, the 
accuracy of the dummy classifier is close to 0.5 for all subject types \todo{Why such variations?}. Random 
Unreal performs very well for all subject types, which confirms that 
ALS is working correctly. Unsurprisingly, all the other methods perform 
better than the dummy classifier, and their accuracy decreases as the 
number of subject types increases.

However, only 3 methods are able to provide accuracy values above 0.85 
for all subject types: Random Subjects (RS), RFNU and RFNTL. This is 
due to the fact that these methods are the only ones that can sample 
files produced toward the end of the execution while maintaining a 
reduced number of empty columns. Surprisingly, RFNTS does not perform 
well for more than 2 subject types, even for a training ratio of 0.9. \todo{Check that.}

@@

\begin{figure*}
\begin{subfigure}[b]{\columnwidth}
        \includegraphics[width=0.8\columnwidth]{data/results/means_of_results/ALS/Synthetic/synthetic_subject_types/ALS-2-types.pdf}
        \caption{2 subject types}
\end{subfigure}
\begin{subfigure}[b]{\columnwidth}
        \includegraphics[width=0.8\columnwidth]{data/results/means_of_results/ALS/Synthetic/synthetic_subject_types/ALS-4-types.pdf}
        \caption{4 subject types}
\end{subfigure}
\begin{subfigure}[b]{\columnwidth}
        \includegraphics[width=0.8\columnwidth]{data/results/means_of_results/ALS/Synthetic/synthetic_subject_types/ALS-8-types.pdf}
        \caption{8 subject types}
\end{subfigure}
\begin{subfigure}[b]{\columnwidth}
        \includegraphics[width=0.8\columnwidth]{data/results/means_of_results/ALS/Synthetic/synthetic_subject_types/ALS-16-types.pdf}
        \caption{16 subject types}
\end{subfigure}
\begin{subfigure}[b]{\columnwidth}
        \includegraphics[width=0.8\columnwidth]{data/results/means_of_results/ALS/Synthetic/synthetic_subject_types/ALS-32-types.pdf}
        \caption{32 subject types}
\end{subfigure}
\hfill
\begin{subfigure}[b]{\columnwidth}
        \includegraphics[width=0.8\columnwidth]{data/results/means_of_results/ALS/Synthetic/synthetic_subject_types/ALS-64-types.pdf}
        \caption{64 subject types}
\end{subfigure}
\caption{Accuracy results on synthetic data, ALS \emph{without} bias.}
\label{fig:results-synthetic}
\end{figure*}

@@

\begin{figure*}
\begin{subfigure}[b]{\columnwidth}
        \includegraphics[width=0.8\columnwidth]{data/results/means_of_results/ALS-Bias/Synthetic/synthetic_subject_types/ALS-Bias-2-types.pdf}
        \caption{2 subject types}
\end{subfigure}
\begin{subfigure}[b]{\columnwidth}
        \includegraphics[width=0.8\columnwidth]{data/results/means_of_results/ALS-Bias/Synthetic/synthetic_subject_types/ALS-Bias-4-types.pdf}
        \caption{4 subject types}
\end{subfigure}
\begin{subfigure}[b]{\columnwidth}
        \includegraphics[width=0.8\columnwidth]{data/results/means_of_results/ALS-Bias/Synthetic/synthetic_subject_types/ALS-Bias-8-types.pdf}
        \caption{8 subject types}
\end{subfigure}
\begin{subfigure}[b]{\columnwidth}
        \includegraphics[width=0.8\columnwidth]{data/results/means_of_results/ALS-Bias/Synthetic/synthetic_subject_types/ALS-Bias-16-types.pdf}
        \caption{16 subject types}
\end{subfigure}
\begin{subfigure}[b]{\columnwidth}
        \includegraphics[width=0.8\columnwidth]{data/results/means_of_results/ALS-Bias/Synthetic/synthetic_subject_types/ALS-Bias-32-types.pdf}
        \caption{32 subject types}
\end{subfigure}
\hfill
\begin{subfigure}[b]{\columnwidth}
        \includegraphics[width=0.8\columnwidth]{data/results/means_of_results/ALS-Bias/Synthetic/synthetic_subject_types/ALS-Bias-64-types.pdf}
        \caption{64 subject types}
\end{subfigure}
\caption{Accuracy results on synthetic data, ALS \emph{with} bias.}
\label{fig:results-synthetic-als-bias}
\end{figure*}

@@

Results for ALS without bias are reported in 
Figure~\ref{fig:results-real-als}. Among the methods that performed 
well in the synthetic dataset, RFNU performs the best, with an accuracy 
higher than 0.95 for all datasets, when the training ratio is larger 
than 0.5. RS and RFNTL are slightly underperforming compared to RFNU. 
Complete rows and complete columns do not even reach the accuracy of 
the dummy classifier. The reference method, Random Unreal, has an 
accuracy close to 1, which shows that collaborative filtering works 
well on this dataset too.
\todo{why is the performance of columns so variable?}

\begin{figure*}
\begin{subfigure}[b]{\columnwidth}
        \includegraphics[width=0.8\columnwidth]{data/results/means_of_results/ALS/PreFreeSurfer/ALS-PFS-5v6.pdf}
        \caption{PFS, CentOS5 vs CentOS6}
\end{subfigure}
\begin{subfigure}[b]{\columnwidth}
        \includegraphics[width=0.8\columnwidth]{data/results/means_of_results/ALS/PreFreeSurfer/ALS-PFS-5v7.pdf}
        \caption{PFS, CentOS5 vs CentOS7}
\end{subfigure}
\begin{subfigure}[b]{\columnwidth}
        \includegraphics[width=0.8\columnwidth]{data/results/means_of_results/ALS/PreFreeSurfer/ALS-PFS-6v7.pdf}
        \caption{PFS, CentOS6 vs CentOS7}
\end{subfigure}\hfill
\begin{subfigure}[b]{\columnwidth}
        \includegraphics[width=0.8\columnwidth]{data/results/means_of_results/ALS/FS-100files/ALS-FS100files.pdf}
        \caption{FS, CentOS6 vs CentOS7}
\end{subfigure}
\caption{Accuracy results on PreFresurfer (PFS) and Freesurfer (FS) data, ALS \emph{without} bias.}
\label{fig:results-real-als}
\end{figure*}

@@

\begin{figure*}
\begin{subfigure}[b]{\columnwidth}
        \includegraphics[width=0.8\columnwidth]{data/results/means_of_results/ALS-Bias/PreFreeSurfer/ALS-Bias-PFS-5v6.pdf}
        \caption{PFS, CentOS5 vs CentOS6}
\end{subfigure}
\begin{subfigure}[b]{\columnwidth}
        \includegraphics[width=0.8\columnwidth]{data/results/means_of_results/ALS-Bias/PreFreeSurfer/ALS-Bias-PFS-5v7.pdf}
        \caption{PFS, CentOS5 vs CentOS7}
        \label{fig:pfs-c5vsc7-bias}
\end{subfigure}
\begin{subfigure}[b]{\columnwidth}
        \includegraphics[width=0.8\columnwidth]{data/results/means_of_results/ALS-Bias/PreFreeSurfer/ALS-Bias-PFS-6v7.pdf}
        \caption{PFS, CentOS6 vs CentOS7}
\end{subfigure}\hfill
\begin{subfigure}[b]{\columnwidth}
        \includegraphics[width=0.8\columnwidth]{data/results/means_of_results/ALS-Bias/FS-100files/ALS-Bias-FS100files.pdf}
        \caption{FS, CentOS6 vs CentOS7}
\end{subfigure}
\caption{Accuracy results on PreFresurfer (PFS) and Freesurfer (FS) data, ALS \emph{with} bias.}
\label{fig:results-real-als-bias}
\end{figure*}
